Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
traffic characteristics section

The censor cannot sniff the content of communications or infer the existence of meek traffic 
from packet \emph{data}, 
since the communication is encrypted inside the TLS session, and we have devoted large efforts 
in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
the existence of meek traffic according to the \emph{meta-data}, i.e. traffic characteristics. 
We studied a collection of traffic characteristics and evaluated their possibilities of becoming
the censor's interest. Specifically, we considered three characteristics: 1) payload length of
TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime. To collect 
the traffic trace of meek, we browsed the Alexa top 500 websites sequentially using the Tor Browser Bundle
and dumped the traffic trace from 
the network interface. We ensured only the browser can successfully access the network by setting
up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
obtained a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. We also
specifically extracted the traffic between LBL and Google. Since the trace only has packet headers, we 
cannot extract the domain information. However, the \texttt{TXT} DNS records of the domain 
\texttt{\_netblocks.google.com} shows the IP address blocks that belongs to Google. Therefore, we 
determine whether a flow is from or to Google by examining the address in the IP header. For this
study we are only interested in Google traffic, because the censor will be mostly likely to compare
suspected meek traffic with normal Google traffic. This part of the trace is 312 MB in size.

@@

Recall that we use browsers to handle HTTPS connections for meek in order to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the meek trace.
In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.

These browser techniques improve performance, but may also lead to unexpected consequences. 
Although meek alters the packet size distribution of underlying Tor traffic, 
the censor may be aware of the distribution of meek itself. 
Additionally, the persistent connection itself can be a problem.
We thus investigated other related characteristics.

>>>>

The censor cannot sniff the content of communications or infer the usage of meek 
from packet \emph{data}, 
since the communication is encrypted inside the TLS session, and we have devoted large efforts 
in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
the existence of meek according to the \emph{meta-data}, i.e. traffic characteristics. 
In this section we study a collection of traffic characteristics and evaluate their possibilities of becoming
the censor's interest. Specifically, we consider three characteristics: 1) payload length of
TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime.

To collect the traffic trace of meek, we browses the Alexa top 500 websites sequentially using 
the Tor Browser Bundle and dump the traffic trace from the network interface. We ensured only
the browser can successfully access the network by setting
up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
obtain a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. 
We also specifically extracted the traffic between LBL and Google from the trace. Since the trace 
only has packet headers, we cannot extract the domain information. However, the \texttt{TXT} DNS
records of the domain \texttt{\_netblocks.google.com} shows the IP address blocks that belongs to
Google. Therefore, we determine whether a flow is from or to Google by examining the address in the 
IP header. We only interested in the Google traffic only, because the censor who wants to defeat meek
will be mostly likely to compare suspicious traffic with normal Google traffic. The size of the 
Google trace is 312 MB.

@@

To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the meek trace.
In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.

These browser techniques improve performance, but also pose unexpected consequences. 
Although meek alters the packet size distribution of underlying Tor traffic, 
the censor may be aware of the distribution of meek itself. 
Additionally, the persistent connection itself can be an issue.
We thus investigated other related characteristics.
